---
title: "Linear models"
author: Purnima Sharma
date: Nov 21, 2020
output: github_document
    
---

```{r setup, include = FALSE}
library(tidyverse)
library(p8105.datasets)

knitr::opts_chunk$set(
  fig.width = 6,
  fig.asp = .6,
  out.width = "90%"
)

theme_set(theme_minimal() + theme(legend.position = "bottom"))

options(
  ggplot2.continuous.colour = "viridis",
  ggplot2.continuous.fill = "viridis"
)

scale_colour_discrete = scale_colour_viridis_d
scale_fill_discrete = scale_fill_viridis_d

set.seed(1)
```

## Import data

```{r}
data("nyc_airbnb")

nyc_airbnb = 
  nyc_airbnb %>% 
  mutate(stars = review_scores_location / 2) %>%  #recoding stars var as review scores
  rename(
    borough = neighbourhood_group,
    neighborhood = neighbourhood) %>%   # renaming these two
  filter(borough != "Staten Island") %>%  # filter out SI since not too many obs
  select(price, stars, borough, neighborhood, room_type)
```

## Fit a model 
(checking how the price of airbnb rental is related to stars, the borough it is in)

```{r}
# doing a visual ck on relationships:
nyc_airbnb %>% 
  ggplot(aes(x = stars, y = price, color = borough)) +
  geom_point()
```

## Let's fit the model we care about 
Want to fit a line that runs through "stars", and maybe different for each borough(categorical predictor).

```{r}
fit = lm(price ~ stars + borough, data = nyc_airbnb)
```

Let's look at the results (these ways not much used).

```{r, include = FALSE}
# include = FALSE because don't want to include these long lists of outputs.

fit      # gives coefficients

summary(fit)   # gives lots more info
summary(fit)$coef  #gives just the coefficients (output is a matrix), or
coef(fit)          #this gives coefficients also, a vector without std.errors n p-values

fitted(fit)  # to get all the fitted values from the model
residuals(fit) #to get all the residuals
```

Let's look at the results better...more organized

```{r}
broom::glance(fit)  # gives all useful one-number summaries, as a tibble

broom::tidy(fit) %>%  #output a tibble, with all coefficients(description in google doc)
  select(-std.error, -statistic) %>%  #don't need these
  mutate(
    term = str_replace(term, "borough", "Borough: ")  #anywhere there is "borough" word,replace with"Borough: "[capital B with a colon and a space], in the var "term".
  ) %>% 
  knitr::kable(digits = 3)    #put it in a nice table, round to 3 decimal places.
```

## Be in control of factors
(looking at dataset, "borough" var is a character var, and very often it gets converted to a factor var, i.e. it gets ordered in alphabetical order. That's why bronx, 1st in order, got to be reference borough by default!)
So, to change reference group (let's say picking one with highest frequency)...

```{r}
nyc_airbnb =                 #overriding dataset
  nyc_airbnb %>% 
  mutate(
    borough = fct_infreq(borough), #mutate borough to factor in order of frequency(most obs).
    room_type = fct_infreq(room_type)  #do same with room_type
  )
```

Look at plot again (with vars as factors vs characters, and ordered per choice)

```{r}
nyc_airbnb %>% 
  ggplot(aes(x = stars, y = price, color = borough)) +
  geom_point()
# now ordered in terms of obs, Manhattan has most obs, followed by Brooklyn, etc.
```

Look at that linear model again

```{r}
fit = lm(price ~ stars + borough, data = nyc_airbnb) 

broom::tidy(fit)  #similar result as in line 59, reference category changed though to manhattan (one with most obs)
```

## Diagnostics

```{r}
#residuals(fit)   :gives a long list of all residuals! takes too much space, 
#instead, modelr package adds a column of residuals to the table of dataset.

modelr::add_residuals(nyc_airbnb, fit) %>%   #input source of data, model used.
  ggplot(aes(x = borough, y = resid)) + #plot residuals vs borough
  geom_violin() +
#gives distribution of residuals in each borough. Except Bronx, all have high resids
  ylim(-500, 1500)   #limiting y-values ro eliminate extreme residuals.

```
OR  (same as above, + plot residuals against "stars (predictors)")
```{r}
nyc_airbnb %>% 
modelr::add_residuals(fit) %>%   
  ggplot(aes(x = borough, y = resid)) + 
  geom_violin() +
  ylim(-500, 1500) 

nyc_airbnb %>% 
  modelr::add_residuals(fit) %>% 
# filter(resid > 5000) %>%      # could do this to check at high-value outlier resids
  ggplot(aes(x = stars, y = resid)) +
  geom_point() +
  facet_wrap(. ~borough)   #facet plots by borough
  
```


## Hypothesis tests

This odes t-test by default

```{r}
fit %>% 
  broom::tidy()  # r does hypothesis test in the background, giving stats & p-values
```

What about the significance of `borough` (all 3 boroughs coefficients at the same time),
F-test(ANOVA) is done (good for multiple comparisons, as compared to doing many t-tests)

```{r}
fit_null = lm(price ~ stars, data = nyc_airbnb) #fit null model of price against stars.
#Null hypothesis: Borough is unassociated with price.

fit_alt = lm(price ~ stars + borough, data = nyc_airbnb)  # alternative model

anova(fit_null, fit_alt) %>%  #use anova to compare models
  broom::tidy()        # tidy the output 
```


# Nest data, fit models

Using interaction terms, this is pretty formal and complex
```{r}
fit = lm(price ~ stars * borough + room_type * borough, data = nyc_airbnb)

broom::tidy(fit)
```

This is more exploratory but easier to understand (nesting).

```{r}
nyc_airbnb %>% 
  nest(data = -borough) %>%    #nest everything except borough.
#will give data organized(into a table) by borough.
#Now we can fit a model to each dataset, for each borough.
mutate(
  models = map(.x = data, ~lm(price ~stars, data = .x)),  #iterating across .x (data)

#mutate adds a column of "models" with lm outcomes as a list-object.  
# %>% pull(models)  : use this to see "models" column. There will be 4 lm fits, one for each borough.
  results = map(models, broom::tidy)   #get "results" column by mapping across "models", and mapping into broom-tidy. Gives better output (vs as a list). Broom tidy will tidy each lm list, and will store it in another list column called "results".
) %>% 
# %>% pull(results)   #to view results column
  
  select(-data, -models) %>% #get rid of these columns, not needed anymore.
  unnest(results) %>%   #perfect output! each borough with its intercept & stars.
  filter(term == "stars")   #don't need intercept, so filter out "stars"
```

Adding room-type to above model.

```{r}
nyc_airbnb %>% 
  nest(data = -borough) %>%    
mutate(
  models = map(.x = data, ~lm(price ~stars + room_type, data = .x)),  
  results = map(models, broom::tidy)  
) %>% 
  select(-data, -models) %>% 
  unnest(results) %>%   
  filter(term != "(Intercept)") %>% 
  select(borough, term, estimate) %>%   #select these columns only.
  pivot_wider(                          # easier to read untidy version.
    names_from = borough,
    values_from = estimate
  )
```


Let's nest even more...
(trying to fit a bunch of lm in every single neighborhood in manhattan)

```{r}
nyc_airbnb %>% 
  filter(borough == "Manhattan") %>% 
  nest(data = -neighborhood) %>%   #nest everything except neighborhood. Will give df for price, stars, room-type for each neighborhood.
  mutate(
  models = map(.x = data, ~lm(price ~stars + room_type, data = .x)),  #will give separate model for each of the 32 neighborhoods.
  results = map(models, broom::tidy)  
) %>% 
  select(-data, -models) %>% 
  unnest(results) %>% 
  filter(str_detect(term, "room_type")) %>%  #interested in coefficient for room-type only. So detect string "room_type" in column "term". Output is "room_type..." only in this column.
  ggplot(aes(x = neighborhood, y = estimate)) + #interested in estimates
  geom_point() +
  facet_wrap(. ~term) + #facet by term, need to fix x-axis labels, so...
  theme(axis.text.x = element_text(angle = 70, vjust = 0.5, hjust = 1))
```

