---
title: "Linear models"
author: Purnima Sharma
date: Nov 21, 2020
output: github_document
    
---

```{r setup, include = FALSE}
library(tidyverse)
library(p8105.datasets)

knitr::opts_chunk$set(
  fig.width = 6,
  fig.asp = .6,
  out.width = "90%"
)

theme_set(theme_minimal() + theme(legend.position = "bottom"))

options(
  ggplot2.continuous.colour = "viridis",
  ggplot2.continuous.fill = "viridis"
)

scale_colour_discrete = scale_colour_viridis_d
scale_fill_discrete = scale_fill_viridis_d

set.seed(1)
```

## Import data

```{r}
data("nyc_airbnb")

nyc_airbnb = 
  nyc_airbnb %>% 
  mutate(stars = review_scores_location / 2) %>%  #recoding stars var as review scores
  rename(
    borough = neighbourhood_group,
    neighborhood = neighbourhood) %>%   # renaming these two
  filter(borough != "Staten Island") %>%  # filter out SI since not too many obs
  select(price, stars, borough, neighborhood, room_type)
```

## Fit a model (checking how the price of airbnb rental is related to stars, the borough it is in)

```{r}
# doing a visual ck on relationships:
nyc_airbnb %>% 
  ggplot(aes(x = stars, y = price, color = borough)) +
  geom_point()
```

## Let's fit the model we care about 
Want to fit a line that runs through "stars", and maybe different for each borough(categorical predictor).

```{r}
fit = lm(price ~ stars + borough, data = nyc_airbnb)
```

Let's look at the results (these ways not much used).

```{r, include = FALSE}
# include = FALSE because don't want to include these long lists of outputs.

fit      # gives coefficients

summary(fit)   # gives lots more info
summary(fit)$coef  #gives just the coefficients (output is a matrix), or
coef(fit)          #this gives coefficients also, a vector without std.errors n p-values

fitted(fit)  # to get all the fitted values from the model
residuals(fit) #to get all the residuals
```

Let's look at the results better...more organized

```{r}
broom::glance(fit)  # gives all useful one-number summaries, as a tibble

broom::tidy(fit) %>%  #output a tibble, with all coefficients(description in google doc)
  select(-std.error, -statistic) %>%  #don't need these
  mutate(
    term = str_replace(term, "borough", "Borough: ")  #anywhere there is "borough" word,replace with"Borough: "[capital B with a colon and a space], in the var "term".
  ) %>% 
  knitr::kable(digits = 3)    #put it in a nice table, round to 3 decimal places.
```

## Be in control of factors
(looking at dataset, "borough" var is a character var, and very often it gets converted to a factor var, i.e. it gets ordered in alphabetical order. That's why bronx, 1st in order, got to be reference borough by default!)
So, to change reference group (let's say picking one with highest frequency)...

```{r}
nyc_airbnb =                 #overriding dataset
  nyc_airbnb %>% 
  mutate(
    borough = fct_infreq(borough), #mutate borough to factor in order of frequency(most obs).
    room_type = fct_infreq(room_type)  #do same with room_type
  )
```

Look at plot again (with vars as factors vs characters, and ordered per choice)

```{r}
nyc_airbnb %>% 
  ggplot(aes(x = stars, y = price, color = borough)) +
  geom_point()
# now ordered in terms of obs, Manhattan has most obs, followed by Brooklyn, etc.
```

Look at tht linear model again

```{r}
fit = lm(price ~ stars + borough, data = nyc_airbnb) 

broom::tidy(fit)  #similar result as in line 59, reference category changed though to manhattan (one with most obs)
```

## Diagnostics







